NanoMaLy

### 2015-11-18 paper/pldi16-submission/evaluation-witness.tex
experimenting with histogram plot while i wait for data...
add some graphs, finally..
trace size graph for seminal
graphs

We ran our search algorithm on each program with the entry point set to
the function that \ocaml had identified as containing a type error. 
%
Due to the possibility of non-termination we set a limit on the number
of reductions to perform, increasing in 1,000-step increments from 1,000
steps to 10,000 steps total.
%
We also added a na\"ive check for infinite recursion; at each recursive
function call we check whether the new arguments are identical to the
current arguments.
%
If so, the function cannot possibly terminate and we report an error.
%
While not a \emph{type error}, infinite recursion is still a clear bug
in the program, and thus valuable feedback for the user.

\begin{figure}[t]
  \centering

  Have a table or graph! \ES{graph of cumulative errors per timeout? \ie
    monotonically increasing, with a cap of 90\% or so}
\caption{Experimental results}
\label{fig:results-witness}
\end{figure}

\paragraph{Results}
\label{sec:results-witness}
The results of our experiments are summarized in
Figure~\ref{fig:results-witness}.
%
In both datasets our tool was able to find a witness for at least XX\%
of the programs.
%
Interestingly, while the vast majority of witnesses corresponded to a
type-error, as expected, X\% triggered an unbound variable error and X\%
triggered an infinite recursion error.
%
XX programs were deemed safe and XX timed out even at 10,000 steps, \ie
we could not provide any useful feedback for XX\% of the total programs.
%
While a more advanced search procedure, \eg dynamic-symbolic execution,
could likely trigger more of the type errors, our experiments show that
type errors are coarse enough (or that novice programs are \emph{simple}
enough) that these techniques are not necessary.

>>>>

We ran our search algorithm on each program with the entry point set to
the function that \ocaml had identified as containing a type error. 
%
Due to the possibility of non-termination we set a limit on the number
of reductions to perform, increasing in 500-step increments from 500
steps to 3,000 steps total.
%
We also added a na\"ive check for infinite recursion; at each recursive
function call we check whether the new arguments are identical to the
current arguments.
%
If so, the function cannot possibly terminate and we report an error.
%
While not a \emph{type error}, infinite recursion is still a clear bug
in the program, and thus valuable feedback for the user.

\begin{figure}[t]
\centering
\begin{minipage}{\linewidth}
\includegraphics[width=\linewidth]{coverage.pdf}
\end{minipage}
\begin{minipage}{\linewidth}
\includegraphics[width=\linewidth]{distrib.pdf}
\end{minipage}
\vspace{-8ex}
\caption{Experimental results. Our random search successfully finds
  witnesses for over 85\% of the programs at the lowest timeout and
  improves slightly to 88\% at the next level. In both datasets we
  detect actual type errors about 82\% of the time, unbound variables or
  constructors 3-4\% of the time, and diverging loops 2-3\% of the
  time. For the remaining 11-12\% of the programs we are unable to
  provide any useful feedback. \ES{TODO: the timeout number for ucsd is
    a bit misleading due to a mistake in the benchmarking code. re-running to fix..}
}
\label{fig:results-witness}
\end{figure}

\paragraph{Results}
\label{sec:results-witness}
The results of our experiments are summarized in
Figure~\ref{fig:results-witness}.
%
In both datasets our tool was able to find a witness for at least XX\%
of the programs.
%
Interestingly, while the vast majority of witnesses corresponded to a
type-error, as expected, X\% triggered an unbound variable error and X\%
triggered an infinite recursion error.
%
XX programs were deemed safe and XX timed out even at 3,000 steps, \ie
we could not provide any useful feedback for XX\% of the total programs.
%
While a more advanced search procedure, \eg dynamic-symbolic execution,
could likely trigger more of the type errors, our experiments show that
type errors are coarse enough (or that novice programs are \emph{simple}
enough) that these techniques are not necessary.
